---
title: "Comparison of the exponential distribution with the Central Limit Theorem"
author: "Mao Soldevilla"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Overview

In this project We are investigating the exponential distribution and compare it with the Central Limit Theorem.
The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda.
lambda was set in 0.2 for all of the simulations.
The distribution of averages of 40 exponentials with thousand simulations.

## Simulations

### Sample Theoretical
We can get the mean and variance from the sample theoretical exponential distribution.
```{r mav}
exp <- rexp(1000, .2)
summary(exp)
var(exp)
```
Theoretically the mean and the standard deviation of any exponential distribution is 1/lambda: `r 1/.2`. Then the mean of our sample distribution is `r mean(exp)` and the standard deviation is `r sd(exp)` that are close to 5 in one simulation.

But if we run a fourteen simulations we can check how the mean and the standard deviation are converging

### comparisons
Whit this chunk of code we can get the vectors of means and variances of 40 simulation in order to compare with the sample.
````{r mean}
mns = NULL
variance = NULL
for (i in 1 : 40){
        s <- rexp(1000, .2)
        mns = c(mns, mean(s))
        variance = c(variance, var(s))
}
```

First we can check the mean versus the sample.
```{r}
hist(mns, main = "Mean", xlab = "Mean")
abline(v = mean(exp), col = "red")
abline(v = mean(mns), col = "blue")

```
As we can see the red line is the mean of the theoretical sample and the blue one is the mean from the 40 simulations.

* According to our simulation we can conclude that the mean is converging to 5 being `r mean(exp)`, and have approximately normal distribution.

Second we can check the variance versus the sample.
```{r}
hist(variance, main = "Variance", xlab = "Variance")
abline(v = var(exp), col = "red")
abline(v = mean(variance), col = "blue")

```
As we can see the red line is the variance of the theoretical sample and the blue one is the mean from the 40 simulations.

* According to our simulation we can conclude that the variance is converging to 25 being the variance of all simulations `r mean(variance)` for then `r sqrt(mean(variance))` the standard deviation close to theoretical, and have approximately normal distribution.