---
title: "Tooth Growth"
author: "Mao Soldevilla"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Overview

In this project we can analyze the ToothGrowth data set included in R package

```{r data}
data("ToothGrowth")
str(ToothGrowth)
```

According our visualization our data frame have sixty obs of three variables.
After that, we will check with summary what kind of data is in.
```{r summary}
summary(ToothGrowth)
```

## Plots for analyse

```{r distribution}
d <- ToothGrowth
g <- ggplot(d, aes(len, color = supp))
g <- g + facet_grid(.~dose)
g <- g + geom_density(size = 1)
print(g)

```
As we can see there are some differences in 0.5 and 1 doses instead of 2.

Now we see the data included in each plot.

## Dose: 0.5

Analyzing the dose = 0.5
```{r}
g1 <- d[d$supp == "OJ" & d$dose == 0.5, ]$len
g2 <- d[d$supp == "VC" & d$dose == 0.5, ]$len
difference <- g2 - g1
mn <- mean(difference)
s <- sd(difference)
n <- length(difference)
mn + c(-1, 1) * qt(.975, n - 1) * s / sqrt(n)
```
The T interval for dose = 0.5

Making a T test
```{r}
t.test(difference)
```
The P-value is `r t.test(difference)$p.value` which is < 0.05, and that means that the dosage supply is *acceptable*

## Dose: 1
Analyzing the dose = 1
```{r}
g1 <- d[d$supp == "OJ" & d$dose == 1, ]$len
g2 <- d[d$supp == "VC" & d$dose == 1, ]$len
difference <- g2 - g1
mn <- mean(difference)
s <- sd(difference)
n <- length(difference)
mn + c(-1, 1) * qt(.975, n - 1) * s / sqrt(n)
```
The T interval for dose = 1

Making a T test
```{r}
t.test(difference)
```
The P-value is `r t.test(difference)$p.value` which is < 0.05, and that means that the dosage supply is *acceptable*

## Dose: 2
Analyzing the dose = 2
```{r}
g1 <- d[d$supp == "OJ" & d$dose == 2, ]$len
g2 <- d[d$supp == "VC" & d$dose == 2, ]$len
difference <- g2 - g1
mn <- mean(difference)
s <- sd(difference)
n <- length(difference)
mn + c(-1, 1) * qt(.975, n - 1) * s / sqrt(n)
```
The T interval for dose = 2

Making a T test
```{r}
t.test(difference)
```
The P-value is `r t.test(difference)$p.value` which is > 0.05, and that means that the dosage supply is *not acceptable*